Combine_results

### 2017-03-10 Code/combine_results.Rmd

```

```{r save_combined_datasets, echo = F}
write.csv(age_cod_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_results.csv")
write.csv(age_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_results.csv")
write.csv(cod_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_decomp_results.csv")
write.csv(BlackWhite_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_results.csv")
write.csv(cod_change_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_change_results.csv")

>>>>

age_decomp_results$widened_gap <- sign(age_decomp_results$age_cont_yrs_mean)
age_decomp_results <- make_pretty_decomp_plot(decomp.table = age_decomp_results, strat.var.1 = "stratum.id", 
                                   partition.bar.var = "age_minbin", sign.var = "widened_gap",
                                   decomp.var = "age_cont_yrs_mean", decomp.var.prop = "age_cont_prop_mean",
                                   type.of.data = "practice")
```

```{r split-age-cod-data-for-save}
age_cod_results_female <- age_cod_results %>% filter(sex == "Female")
age_cod_results_male <- age_cod_results %>% filter(sex == "Male")
```

```{r save_combined_datasets, echo = F}
write.csv(age_cod_results_female, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_results_female.csv")
write.csv(age_cod_results_male, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_results_male.csv")
write.csv(age_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_results.csv")
write.csv(cod_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_decomp_results.csv")
write.csv(BlackWhite_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_results.csv")
write.csv(cod_change_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_change_results.csv")
